---
title: "HW 4"
author: "Namrata Ray, Jugal Marfatia, Md Muhtasim Billah"
date: "11/14/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1

## Importing the data

```{r warning=FALSE, message=FALSE}
#setting working directory
setwd("/Users/muhtasim/Desktop/myRfolder/ling")
getwd()
# check content of working directory
dir()
#loading the necessary libraries
library(limma)
library(affy)
#reading the data
abatch=ReadAffy()
```

## Writing the design and contrast matrix

```{r warning=FALSE, message=FALSE}
#design matrix for the given problem
#limma writes the design matrix columnwise
design=matrix(c(1,1,0,0,0,0,0,0,0,0,1,1,0,0,0,0,0,0,0,0,1,1,0,0,0,0,0,0,0,0,1,1),nrow=8)
design

#defining the contrast matrix for the given problem
contrastMatrix=matrix(c(
  + 1,1,-1,-1,
  + -1,1,-1,1,
  + 1,-1, -1,1),nrow=ncol(design))
contrastNames=c("DOM-WT","M-F","INT")   
#INT=interaction,M-F=male-female,DOM-WT=domesticated/wild-type
colnames(contrastMatrix)=contrastNames
contrastMatrix
```

## Analyzing the data
```{r warning=FALSE, message=FALSE}
#normalizing the data
eset=rma(abatch)
#using linear model and design matrix to fit the data
fit=lmFit(eset,design=design)
#calculating the contrasts to compare among trts
fit2=contrasts.fit(fit,contrasts=contrastMatrix)
names(fit2)
#empirical Bayes' fit  
fit3=eBayes(fit2)
```

## Plotting the top tables using FDR

```{r warning=FALSE, message=FALSE}
#getting the toptable
topTable(fit3,coef="DOM-WT",adjust="fdr")

topTable(fit3,coef="M-F",adjust="fdr")

topTable(fit3,coef="INT",adjust="fdr")
```

## Showing the Venn diagram to show the genes in common

```{r warning=FALSE, message=FALSE}
F.stat=fit3$F
p.value=fit3$F.p.value
results=classifyTestsF(fit3,p.value=1.0E-2)
#Venn Diagram of results
vennDiagram(results,names=c("DOM-WT","M-F","INT"))
```



\section{Question 2}
\begin{tabular}{llllllll}
\hline
\multicolumn{1}{|l|}{A1B1} & \multicolumn{1}{l|}{A2B1} & \multicolumn{1}{l|}{A1B2} & \multicolumn{1}{l|}{A2B2} & \multicolumn{1}{l|}{A1B3} & \multicolumn{1}{l|}{A2B3} & \multicolumn{1}{l|}{A1B4} & \multicolumn{1}{l|}{A2B4} \\ \hline
1                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
1                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 1                         & 0                          \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 1                          \\

0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 1                       \\
\hline
\end{tabular}

The Contrast matrix 1 is : (1, -1, 0, 0, 0, 0, 0, 0)
The Contrast matrix 2 is : (-1/6, -1/6, -1/6, -1/6, 1/2, 1/2, -1/6, -1/6)

\newpage
\section{Question 3}
\begin{tabular}{llllllll}
\hline
\multicolumn{1}{|l|}{A1B1C1} & \multicolumn{1}{l|}{A1B1C2} & \multicolumn{1}{l|}{A1B2C1} & \multicolumn{1}{l|}{A1B2C2} & \multicolumn{1}{l|}{A2B1C1} & \multicolumn{1}{l|}{A2B1C2} & \multicolumn{1}{l|}{A2B2C1} & \multicolumn{1}{l|}{A2B2C2} \\ \hline
1                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
1                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 1                         & 0                         \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 1                         & 0                          \\
0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 1                         \\

0                          & 0                         & 0                         & 0                         & 0                         & 0                         & 0                         & 1                       \\
\hline

\end{tabular}

