---
title: "Homework 2"
author: "Jugal Marfatia, Namrata Ray, Md Muhtasim Billah"
date: "10/01/2019"
output: pdf_document
---
## Question 1

I have put the data set loess2.csv on the website.  Use the data to run loess plots using spans of .1, .3, .5, .7 and .9.  Give the loess plot with the different spans using the lines option in R.

```{r}
data=read.csv("loessdata2.csv",header=TRUE)
#head(data)
y1=data$x2
y2=data$y2
M=y1-y2
A=(y1+y2)/2

plot(y1,y2)
plot(A,M)

#loess plots with the different spans

j <- order(A)

lw1 <- loess(M ~ A,data=data,span=0.10)
lw2 <- loess(M ~ A,data=data,span=0.30)
lw3 <- loess(M ~ A,data=data,span=0.50)
lw4 <- loess(M ~ A,data=data,span=0.70)
lw5 <- loess(M ~ A,data=data,span=0.90)

#plotting all the lines together

plot(M ~ A, data=data)
lines(A[j],lw1$fitted[j],col="red",lwd=3)
lines(A[j],lw2$fitted[j],col="green",lwd=3)
lines(A[j],lw3$fitted[j],col="blue",lwd=3)
lines(A[j],lw4$fitted[j],col="yellow",lwd=3)
lines(A[j],lw5$fitted[j],col="brown",lwd=3)
```


## Question 2

Consider the following are data from 3 arrays 6 spots each.  Give the quantile-normalized array values.

```{r}
array1 = c(5.390,	12.074,		3.247,		4.274,		11.24,	14.861)
array2 = c(5.813,	 8.777,		2.914,		2.736,		6.398,	23.020)
array3 = c(7.522,	 7.719,		1.783,		10.59,		4.439,	21.972)

array1_s = sort(array1) 
array2_s = sort(array2) 
array3_s = sort(array3)

matrix = rbind(c(5.390,	12.074,		3.247,		4.274,		11.24,	14.861),
               c(5.813,	 8.777,		2.914,		2.736,		6.398,	23.020),
               c(7.522,	 7.719,		1.783,		10.59,		4.439,	21.972))

matrix_s = rbind(array1_s, array2_s, array3_s) 
c_means = colMeans(matrix_s)


for(i in 0:length(array1_s)+1){
  matrix[matrix == array1_s[i]] = c_means[i]
  matrix[matrix == array2_s[i]] = c_means[i]
  matrix[matrix == array3_s[i]] = c_means[i]
}
matrix
```


## Question 3

I have put the data set for the craig.zip on the website.  Download the files and do M versus A plots, boxplots and histograms with and without normalization.  Use the methods discussed in class, MAS5 and RMA for normalization.

```{r message=FALSE}
library(affyPLM)
library(preprocessCore)
a.data=ReadAffy()
```

### Boxplot without normalization
```{r warning=FALSE}
boxplot(a.data)
```


### Histogram without normalization
```{r}
hist(a.data,col=0:6,main="Histogram of probe intensities")
```


### MAplot without normalization
```{r}
par(mfrow=c(2,3))
MAplot(a.data)
```


### Boxplot with MAS5 normalization
```{r}
eset.mas5=mas5(a.data)
boxplot(eset.mas5)
```


### Histogram with MAS5 normalization
```{r}
hist(eset.mas5,col=0:6,main="Histogram of probe intensities")
```

### MAplot with MAS5 normalization
```{r}
par(mfrow=c(2,3))
MAplot(eset.mas5)
```

### Boxplot with RMA  normalization
```{r}
eset.rma=rma(a.data)
boxplot(eset.rma)
```

### Histogram with RMA  normalization
```{r}
hist(eset.rma,col=0:6,main="Histogram of probe intensities")
```


### MAplot with RMA  normalization
```{r}
par(mfrow=c(2,3))
MAplot(eset.rma)
```


### Question 2 From Homework 1. Tukey Biweight method  

```{r}
df = read.csv("/Users/muhtasim/Desktop/HW1/hw1.csv")

y= log2(df$PM1) - log2(df$MM1)

md<-median(y)

z<-abs(y-md)

mz<-median(z)

u<-(y-md)/(5*mz+.0001)
w<-ifelse(abs(u)<=1,(1-u^2)^2,0)
table.data=cbind(y,md,z,mz,u,w)
tuk_avg=sum(y*w)/sum(w)
tuk_avg
```
## Signal 
```{r}
IM<-ifelse(df$MM1>df$PM1,df$PM1/(2^tuk_avg),df$MM1)
i1<-IM
ys<-log2(df$PM1-i1)
ms<-median(ys)
zs<-abs(ys-ms)
ss<-median(zs)
us<-(ys-ms)/(5*ss+.0001)
ws<-ifelse(abs(us)<=1,(1-us^2)^2,0)
tbs<-sum(ws*ys)/sum(ws)
sgnl<-2^tbs
sgnl
```